Analysis of competitive surfing tournaments with generalized Bradley-Terry likelihoods

### 2022-09-25 inst/surfing.Rmd
fixes #171

>>>>

```{r, directplotofstengths}
pdf(file="directplotofstrengths.pdf")
par(xpd=NA)
plot(jjO,jjL,pch=16,log='y',xlab='points',ylab='maximum likelihood strength',cex=1.5)
fit <- lm(log10(jjL)~(jjO))
summary(fit)
for(i in seq_along(jjO)){
text(jjO[i],jjL[i],names(jjL)[i],col='gray',pos=4,cex=0.8)
}
par(xpd=FALSE)
abline(fit)
dev.off()
```

### 2022-09-25 inst/surfing_jsa.tex
fixes #171

However, points awarded may be compared with likelihood estimates, and
one would expect high points totals to be associated with high
likelihoods.  Figure~\ref{compare_likelihood_points} shows a loose
correlation ($R^2=0.64$; $p=3\times 10^{-6}$) and
Figure~\ref{compare_likelihood_points_rankings} shows how the rankings
differ when calculated by the points and likelihood systems.  Note the
anomalous position of Florence, who did not compete in five venues due
to injury: this strongly affecting his points total but not his
likelihood-based ranking.

>>>>

However, points awarded may be compared with likelihood estimates, and
one would expect high points totals to be associated with high
likelihoods.  Figure~\ref{compare_likelihood_points} shows a loose
correlation ($R^2=0.71$; $p=4\times 10^{-7}$) and
Figure~\ref{compare_likelihood_points_rankings} shows how the rankings
differ when calculated by the points and likelihood systems.  Note the
anomalous position of Florence, who did not compete in five venues due
to injury: this strongly affecting his points total but not his
likelihood-based ranking.
